\textbf{The Heart can Lie: The Role of Interoception and Theory of Mind in Deception}

### 2023-04-23 paper/manuscript.Rmd
fix fig caption

```{r message=FALSE, warning=FALSE, out.width="100%", fig.cap="Interindividual corrrelates of lying confidence. The lines shows the relationship (with 95% CI uncertainty), assessed via Bayesian mixed models (**pd > 97%, **pd > 99%, ***pd > 99.9%), between the participants' interoceptive and theory of mind composite scores and the confidence ratings of their lies and truthful asnwers. Their average lying confidence (+/- 1 SD), withing the two experimental conditions, is displayed as points for descriptive purposes (as the models were ran on individual trials)."}
knitr::include_graphics("../figures/figure1.png")
```

>>>>

```{r message=FALSE, warning=FALSE, out.width="100%", fig.cap="Interindividual corrrelates of lying confidence. The lines shows the relationship (with 95\\% CI uncertainty), assessed via Bayesian mixed models (\\***pd > 97\\%, \\***pd > 99\\%, \\****pd > 99.9\\%), between the participants' interoceptive and TOM composite scores and the confidence ratings of their responses. Average lying confidence (+/- 1 SD) within the two experimental conditions is displayed as points for descriptive purposes as the models were ran on individual trials."}
knitr::include_graphics("../figures/figure1.png")
```

### 2023-04-23 paper/manuscript.tex
fix fig caption

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\usepackage[labelfont=bf, font={color=gray,small}]{caption}
\usepackage{float}
\usepackage[document]{ragged2e}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={The Heart can Lie: The Role of Interoception and Theory of Mind in Deception},
  pdfauthor={Dominique Makowski1, 2, Zen J. Lau2, Tam Pham2, An Shu Te2, Stephanie Kirk2, Claudia Liauw2, \& S.H. Annabel Chen2, 3, 4, 5},
  pdflang={en-EN},
  pdfkeywords={Deception, Interoception, Theory of Mind, Poygraph, Lying Ability},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\textbackslash begin\{figure\}
\includegraphics[width=1\linewidth]{../figures/figure1} \textbackslash caption\{Interindividual corrrelates of lying confidence. The lines shows the relationship (with 95\% CI uncertainty), assessed via Bayesian mixed models (\textbf{pd \textgreater{} 97\%, }pd \textgreater{} 99\%, ***pd \textgreater{} 99.9\%), between the participants' interoceptive and theory of mind composite scores and the confidence ratings of their lies and truthful asnwers. Their average lying confidence (+/- 1 SD), withing the two experimental conditions, is displayed as points for descriptive purposes (as the models were ran on individual trials).\}\label{fig:unnamed-chunk-1}
\textbackslash end\{figure\}

@@

\leavevmode\vadjust pre{\hypertarget{ref-chen2021emerging}{}}%
Chen, W. G., Schloesser, D., Arensdorf, A. M., Simmons, J. M., Cui, C., Valentino, R., Gnadt, J. W., Nielsen, L., Hillaire-Clarke, C. S., Spruance, V., et al. (2021). The emerging science of interoception: Sensing, integrating, interpreting, and regulating signals within the self. \emph{Trends in Neurosciences}, \emph{44}(1), 3--16.

@@

\leavevmode\vadjust pre{\hypertarget{ref-yoris2015roles}{}}%
Yoris, A., Esteves, S., Couto, B., Melloni, M., Kichic, R., Cetkovich, M., Favaloro, R., Moser, J., Manes, F., Ibanez, A., et al. (2015). The roles of interoceptive sensitivity and metacognitive interoception in panic. \emph{Behavioral and Brain Functions}, \emph{11}(1), 1--6.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={The Heart can Lie: The Role of Interoception and Theory of Mind in Deception},
  pdfauthor={Dominique Makowski1, 2, Zen J. Lau2, Tam Pham2, An Shu Te2, Stephanie Kirk2, Claudia Liauw2, \& S.H. Annabel Chen2, 3, 4, 5},
  pdflang={en-EN},
  pdfkeywords={Deception, Interoception, Theory of Mind, Poygraph, Lying Ability},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\usepackage[labelfont=bf, font={color=gray,small}]{caption}
\usepackage{float}
\usepackage[document]{ragged2e}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

\begin{figure}
\includegraphics[width=1\linewidth]{../figures/figure1} \caption{Interindividual corrrelates of lying confidence. The lines shows the relationship (with 95\% CI uncertainty), assessed via Bayesian mixed models (\***pd > 97\%, \***pd > 99\%, \****pd > 99.9\%), between the participants' interoceptive and TOM composite scores and the confidence ratings of their responses. Average lying confidence (+/- 1 SD) within the two experimental conditions is displayed as points for descriptive purposes as the models were ran on individual trials.}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\leavevmode\vadjust pre{\hypertarget{ref-chen2021emerging}{}}%
Chen, W. G., Schloesser, D., Arensdorf, A. M., Simmons, J. M., Cui, C., Valentino, R., Gnadt, J. W., Nielsen, L., Hillaire-Clarke, C. S., Spruance, V.others. (2021). The emerging science of interoception: Sensing, integrating, interpreting, and regulating signals within the self. \emph{Trends in Neurosciences}, \emph{44}(1), 3--16.

@@

\leavevmode\vadjust pre{\hypertarget{ref-yoris2015roles}{}}%
Yoris, A., Esteves, S., Couto, B., Melloni, M., Kichic, R., Cetkovich, M., Favaloro, R., Moser, J., Manes, F., Ibanez, A.others. (2015). The roles of interoceptive sensitivity and metacognitive interoception in panic. \emph{Behavioral and Brain Functions}, \emph{11}(1), 1--6.
